---
title: "encryptr"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE}
library(tidyverse)
library(encryptr)
```


To use, clone directory to deskop folder and unzip there as well,
Open the .Rprog file to open project and run


```{r eval=FALSE, include=TRUE}
source('data-raw/index.R')
```


This chunk of code creates a file data/password_hash_table.rda in your project folder 
which would hold the index table for the encryption process, in this tutorial, we would 
be using this package would be to store passwords and create hash characters

However, if you would like an end-to-end encyption process, for text, files, etc you
could get in touch with me [here](mailto:edgarjohn95@gmail.com) 

To ensure every user has an absolutely different set of rules for the program, 
you would first have to generate your index table yourself assigning values to
alphanumeric characters from a random selection of 1000 possible values by running

From the tabs at the top of RStudio IDE, Click on Build, and click on Install and Restart.
This would build the package on your machine and install it 

This package is used to create hash characters. Example usage include:

- encrypt user passwords to provide extra security
- create hash ids for blockchain transactions 


### user passwords


Let's create a function that takes in a username and a password and returns a 
row of data with username and encrypted password


```{r example_user}
store_user_data <- function(username, password){
  data.frame(
    username = username,
    encrypted_password = encrypt(password),
    # ensures values are stored as characters and not factored 
    stringsAsFactors = F
  )
}

# call store_user_data on user with username:new_user & password:password123
# store the result in an object, example_user
example_user <- store_user_data("new_user", "password123")

example_user
```


In this case, your program takes in a password in plain text and encrypts it before 
it searches the dataframe. 


In a case where your dataframe is leaked, and the 
encrypted password is passed as a parameter, authentication would fail. 
To show the value that would be returned in this case, you could run 


```{r}
user_login_data <- data.frame(
  # generate a list of users from user1 to user 10
  username = paste("user", 1:10, sep = ""),
  # create random passwords by adding a random 4 digit number to "pass"
  password = paste("pass", 
                   sample(1000:9999, 10) %>% as.character(),
                   sep = ""
                   ),
  stringsAsFactors = F
) %>% mutate(encrypted_password = purrr::map_chr(password, encrypt))

user_login_data

user_authentication <- function(username, password){
  # get password from user and encrpyt before data is sent from user
  password <- encrypt(password)
  # search user login dataframe and check is password matches selected user
  user_login_data[user_login_data$username == username & user_login_data$encrypted_password == password,] %>% select(username, encrypted_password)
}


# This would be a situation where encrypt is called twice on a password
encrypt_twice <- function(x)encrypt(x) %>% encrypt()

once <- user_login_data[1,]$encrypted_password
twice <- once %>% encrypt_twice()
list(# list out user1 details
     as.list(user_login_data[1,]),
     # raw text of calling this function twice
     encrypt_twice = twice, 
     # search table for when user enters ...
     # password used to sign up
     search = user_authentication("user1", user_login_data$password[1]),
     # password from main database
     search = user_authentication("user1", twice),
     # password with caps lock on
     search = user_authentication("user1", once %>% toupper()),
     # miss the last character?
     search = user_authentication("user1", once %>% substr(1,7)),
     # miss the last character?
     search = user_authentication("user1", once %>% substr(2,8))
     )
```


## hash ids for blockchain transactions


In a case where you would want to use the program to create unique hash ids for transactions,
you could use the encrypt function to generate ids, You might ask why not just use sys.time()
as an id? If another user has access to a timeframe that a transaction was performed, it is 
easier to find the transaction id assuming it's to be kept secret

If you would like to use this reproducibly, it is recomended you get the id once and send the
ids to both parties

Here's an example of seven transactions made exactly 4 hours apart from each other, even when 
transaction times are very similar, you could still see the difference in the ids

```{r}
transact_times <- c(
  Sys.time() - 8.64e04,
  Sys.time() - 7.20e04,
  Sys.time() - 5.76e04,
  Sys.time() - 4.32e04,
  Sys.time() - 2.88e04,
  Sys.time() - 1.44e04,
  Sys.time()
)

data.frame(
  Timestamp = map_chr(transact_times, prettydates::short_dt12_us_w),
  Id = map_chr(transact_times, encrypt),
  stringsAsFactors = F
)
```


















